Bird beak's elaboration and innovation

### 2022-08-04 Analysis/04-Figure3_with_ellipse_scalling_and_8D_histograms.Rmd
Update 04-Figure3_with_ellipse_scalling_and_8D_histograms.Rmd

```{r, eval = TRUE, echo = FALSE}
box_size <- 1.5
pdf(file = "../Manuscript/Figures/Figure3_ellipses.pdf", height = box_size*10, width = box_size*10)

@@

```{r}
box_size <- 1.5
pdf(file = "../Manuscript/Figures/Figure3_passeriformes.pdf", height = box_size*9, width = box_size*10)

>>>>

```{r, eval = TRUE, echo = FALSE}
## Get the bar plots for the loadings of the phylogeny component
# pdf(file = "../Manuscript/Figures/phylo_loadings.pdf", height = 4, width = 4)
# plot(NULL, xlim = range(superorder_shapespace$matrix), ylim = range(superorder_shapespace$matrix))
# add.dims(superorder_shapespace, name.col = c(phylogeny = "grey"), n = 1000)
# dev.off()

box_size <- 1.5
pdf(file = "../Manuscript/Figures/Figure3_ellipses.pdf", height = box_size*10, width = box_size*10)

@@

```{r}
## Adding the bar plot for the phylogeny component
# pdf(file = "../Manuscript/Figures/phylo_loadings.pdf", height = 4, width = 4)
# plot(NULL, xlim = range(suborder_shapespace$matrix), ylim = range(suborder_shapespace$matrix))
# add.dims(suborder_shapespace, name.col = c(phylogeny = "grey"), n = 1000)
# dev.off()

box_size <- 1.5
pdf(file = "../Manuscript/Figures/Figure3_passeriformes.pdf", height = box_size*9, width = box_size*10)
